---
title: "Code Comments"
author: "Francis R. Kovacs"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
urlcolor: blue
vignette: >
  %\VignetteIndexEntry{Code Comments}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(cmu202)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.width = 7,
  height = 6
)
```

When writing R code, good comments are essential. Code comments are pieces of text that are not executed and serve as notes to describe what the code is doing. Comments serve to guide a reader through perhaps unfamiliar code. In general, code comments allow you to look at code from over six months ago and reason through the code. 

Comments are denoted in R by one or more `#` in a line by itself. Observe the code below:

```{r, echo=TRUE, eval=FALSE}
library(cmu202)
cat("This is text")
# Load the library and print some text

y <- 1356

### Comments can have multiple #s starting the lines

x <- 5 # A comment with code 
```

Note that in each line, everything after `#` is considered a comment. Also note that when knitting to `.pdf` and `.html` output, the comments with multiple `#`s seem to appear different in the output, yet are functionally identical to comments that begin with a single `#`. 

