---
title: "R Packages"
author: "Francis R. Kovacs"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
urlcolor: blue
vignette: >
  %\VignetteIndexEntry{R Packages}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(R202)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.width = 7,
  height = 6
)
```

## Packages

The functionality of R is bolstered by user-developed segments of code known as packages. While base R is installed with 15 required packages, thousands of packages are created each year to streamline complicated processes in a reproducible manner. In a package the author will create _functions_, blocks of code that perform a specific task for a certain input. Such functions remove the burden of calculation from the user -- allowing long calculations such as least squares regression to be done in a matter of seconds with no programming knowledge. Packages also contain data sets -- as such data is now stored in a single location. 

## Installation and Loading

One can install R packages to their computer with a single call, after which the package may be loaded for use at any time thereafter. One must load each installed package with the `library()` command to then use the package. This mechanism is designed to not create a memory burden on the computer -- as the package will then take up space in the environment after being loaded. 

To summarize:

Package must only be installed once. For example:

```{r, echo=TRUE, eval=FALSE}
# This example is incredibly bad style, as you would always install a package in the terminal

install.packages("ggplot2")
```

To load `ggplot2` in a new R session, one must run (at the start of each file that uses the package):

```{r echo=TRUE, eval=FALSE}
library(ggplot2)
```

Typically most `library()` calls are performed at the top of each `.R` or `.Rmd` file. For an `.Rmd` file, the `library()` calls are performed in the first code chunk -- making them available for all following code chunks. 

**One must load each needed package at the start of every file**

## Package Management

To view the installed packages, one may explore the "packages" tab in the lower-right pane. From this location the user may view documentation, install new packages and remove packages. For new users, this interface is highly recommended for the installation of packages. 

