---
title: "Viewing Data"
author: "Francis R. Kovacs"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
urlcolor: blue
vignette: >
  %\VignetteIndexEntry{Viewing Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(cmu202)
library(ggplot2)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  eval=FALSE,
  fig.width = 7,
  height = 6
)
```

# Viewing Data

## View

When you have a dataframe (an entry under the "data" tab of "environment"), you may view it in an excel-like format by running the following code:

```{r, echo=TRUE, eval=FALSE}
View(data_name)
```

Note that this command is never to be run in an `.Rmd` or `.R` file, only in the terminal.

## Head

The `head()` function allows one to see the first 6 rows of data. It is called with:

```{r, eval=TRUE}
# Load the data for the example
library(cmu202)
data("airlines")

head(airlines)
```

## Tail

The `tail()` function allows one to see the last six rows of data. It is called with:

```{r, eval=TRUE}
# Load the data for the example
library(cmu202)
data("airlines")

tail(airlines)
```


